Convex optimisation in communications with cvxpy

### 2017-07-17 article_cvxpy.tex
test
introduction made better

Here we show that many interesting problems in communications not only have a convex formulation (as shown in \cite{cvxpybook}), but can be easily implemented computationally using the \texttt{cvxpy} programming language. The ease of implementation of such problems makes \texttt{cvxpy} an invaluable tool for both students and researchers in many areas of science and engineering.
\subsection{Convex Sets and Functions}

>>>>

Here we show that an interesting problem in communications not only has a convex formulation (as shown in \cite{cvxpybook}), but can be easily implemented computationally using the \texttt{cvxpy} Python module. The ease of implementation makes \texttt{cvxpy} an invaluable tool for both students and researchers in many areas of science and engineering.
\subsection{Convex Sets and Functions}
